The Effects of Varying Depth in Cosmic Shear Surveys

### 2019-05-08 discussion.tex
Added cosmology dependency

>>>>

While the cosmology dependency (compare Fig. \ref{fig:comparecosmo}) is not significant for the KV450 survey, it will be relevant for the Euclid survey. In that case, a calculation of the correction for this effect is necessary for every cosmology in the MCMC simulation, underlining the necessity for a fast, analytic model.

### 2019-05-08 paperdraft.tex
Added cosmology dependency

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe. The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Especially ground-based surveys are subject to a variation in depth. We want to understand and quantify the resulting effects. In particular, we check whether they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters. Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$. However, the parameter $S_8$ is robust against this modification. We also report the occurrence of B-Modes, although not to a significant degree.
% conclusions (optional)
   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}

>>>>

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the local Universe. The discrepancy in the parameter $S_8$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Especially ground-based surveys are subject to a variation in depth. We want to understand and quantify the resulting effects. In particular, we check whether they introduce a bias to the cosmological parameters and if they can be responsible for the occurence of $B$-Modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation function and analyze the implications for cosmological parameters. Furthermore we construct COSEBIs of the correlation functions to quantify the occuring B-Modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$. However, the parameter $S_8$ is robust against this modification. We find that the dependency of this effect on the underlying cosmology is not neglible. We also report the occurrence of B-Modes, although not to a significant degree.
% conclusions (optional)
   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments. Due to the cosmology dependency, further analyses require a fast, analytic model for this effect.}
